BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-10 tex/4-techniques.tex
Fix/respond to all comments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used language for client-side scripting. While some applications simply use it for aesthetics (menus, animations, \ldots), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawlers do not see\comment{instead of see, maybe interpret, understand, render?} web pages as they are presented to a human visitor\comment{coninuing the previous comment: ...as they are presented to a human visitor by a web browser} and might therefore be obsolete for data extraction.

% Motivation
In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services. For webmasters\comment{I think web-master is officially one word without the hyphen}, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.

% The solution
To support blogs with JavaScript-generated content, we embed a full web browser into the crawler. After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performance and scripting capabilities. The JavaScript rendering is the very first step of web page processing. Therefore, extracting blog post articles, comments or medias\comment{do you mean multimedia files? media is rather a concept in English and does not exist in plural} works equally well on blogs with JavaScript-generated content as well as on traditional HTML-only blogs.

% Click click scripting
When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} button. As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained. They constitute the only non-generic element of our extraction stack which requires human intervention to maintain and extend to other commenting platforms.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog. After being downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download media\comment{as before, media is rather a concept. Should we replace with multimedia files?}
  \item Propagate resulting records to the back end
\end{enumerate}
This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}\label{enrichingscrapy}
% into
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of blog pages holding\comment{maybe replace "holding" with: "which are"} blog posts: \emph{blog post identification} and \emph{download priority heuristic}.

% blog post identification
Given an entry point to a website\comment{entry point == URL, right? Maybe clarify that here?}, the default Scrapy behavior looks over\comment{instead of "looks over" maybe "goes through" or "traverses" or "parses" or "looks at". Not sure, need some english-speaking person's opinion} all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the URLs found in the web feed for each entry\comment{this last sentence has been slightly rephrased. Please check that it still makes sense they way you want it.}. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers\comment{is a reference needed here?}.

% download priority heuristic
In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient. Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts\comment{replace "non-blog-post" with "all other". Is that OK?}. To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system. This mechanism has shown to be mandatory for blogs hosted on a single domain alongside large number of other types of web pages, such as those in forums or wikis.

% Distance-Weighted k-Nearest-Neighbor
The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$\comment{rephrased this last sentence slightly. Please make sure that it still makes sense.}.

@@

Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high-level point of view, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
%
where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator. By delegating all shared mutable state to the back end system (Invenio's database)\comment{this is the 1st mention of Invenio. Make sure to mention in the Introduction, or remove from here as well.}, web crawler instances can be added, removed and used interchangeably.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used language for client-side scripting. While some applications simply use it for aesthetics (menus, animations, \ldots), an increasing number of websites use JavaScript to download and display content. In such cases, traditional HTML based crawlers do not see\comment{instead of see, maybe interpret, understand, render?}\TODO{I think I like the "see" better, even if it's informal it really transmits primary motivation for this JS rendering.} web pages as they are presented to a human visitor by a web browser, and might therefore be obsolete for data extraction.

% Motivation
In our experiments whilst crawling the blogosphere, we encountered several blogs where crawled data was incomplete because of the lack of JavaScript interpretation. The most frequent cases were blogs using the Disqus \cite{disqus2013} and LiveFyre \cite{livefyre2013} comment hosting services. For webmasters, these tools are very handy because the entire comments infrastructure is externalized and their setup essentially comes down to including a JavaScript snippet in each target page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time updates for edits and newly written comments. Less commonly, some blogs are fully rendered using JavaScript. When loading such websites, the web browser will not receive the page content as an HTML document, but will instead have to execute JavaScript code to download and display the page content. The Blogger platform provides the \emph{Dynamic Views} as a default template, which uses this mechanism \cite{antinharasymiv2011}.

% The solution
To support blogs with JavaScript-generated content, we embed a full web browser into the crawler. After considering multiple options, we opted for PhantomJS \cite{phantomjs2013}, a headless web browser with great performance and scripting capabilities. The JavaScript rendering is the very first step of web page processing. Therefore, extracting blog post articles, comments or multimedia files works equally well on blogs with JavaScript-generated content and on traditional HTML-only blogs.

% Click click scripting
When the number of comments on a page exceeds a certain threshold, both Disqus and LiveFyre will only load the most recent ones and the stream of comments will end with a \emph{Show More Comments} button. As part of the page loading process, we instruct PhantomJS to repeatedly click on these buttons until all comments are loaded. Paths to Disqus and LiveFyre \emph{Show More} buttons are manually obtained. They constitute the only non-generic elements of our extraction stack which require human intervention to maintain and extend to other commenting platforms.

@@

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which implement the logic to respectively crawl a new blog and get updates from a previously crawled blog. After being downloaded and identified as blog posts (details in \ref{enrichingscrapy}), pages are packed into \emph{Items} and sent through the following pipeline of operations:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download multimedia files
  \item Propagate resulting records to the back end
\end{enumerate}
This pipeline design provides great modularity. For example, disabling JavaScript rendering or plugging in an alternative back-end can be done by editing one single line of code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}\label{enrichingscrapy}
% into
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process down to the subsets of pages which are blog posts: \emph{blog post identification} and \emph{download priority heuristic}.

% blog post identification
Given an URL entry point to a website, the default Scrapy behavior traverses all the pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify whether a URL points to a blog post or not. Internally, for each blog, this function uses a regular expression constructed from the blog post URLs found in the web feed. This simple approach requires that blogs use the same URL pattern for all their posts (or false negatives will occur) which has to be distinct for pages that are not posts (or false positives will occur). In practice, this assumption holds for all blog platforms we encountered and seems to be a common practice amongst web developers\comment{is a reference needed here?}\TODO{Isn't the "seems" enought? (I never encontered a blog where this is not the case...)}.

% download priority heuristic
In order to efficiently deal with blogs that have a large number of pages which are not posts, the \emph{blog post identification} mechanism is not sufficient. Indeed, after all pages identified as blog posts are processed, the crawler needs to download all other pages to search for additional blog posts. To replace the naive \emph{random walk}, \emph{depth first search} or \emph{breadth first search} web site traversals, we use a priority queue where priorities for new URLs are determined by a machine learning system. This mechanism has shown to be mandatory for blogs hosted on a single domain alongside large number of other types of web pages, such as those in forums or wikis.

% Distance-Weighted k-Nearest-Neighbor
The idea is to give high priority to URLs which are believed to point to pages with links to blog posts. These predictions are done using an active \emph{Distance-Weighted k-Nearest-Neighbor} classifier \cite{dudani1976}. Let $L(u)$ be the number of links to blog posts contained in a page with URL $u$. Whenever a page is downloaded, its URL $u$ and $L(u)$ are given to the machine learning system as training data. When the crawler encounters a new URL $v$, it will ask the machine learning system for a estimation of $L(v)$, and use this value as the download priority of $v$. $L(v)$ is estimated by calculating a weighted average of the values of the $k$ URLs most similar to $v$.

@@

Heading in this direction, we made the key design choice to have both \emph{NewCrawl} and \emph{UpdateCrawl} as stateless components. From a high-level point of view, these two components are \emph{purely functional}:
%
\newcommand\URL{\mathbb{U}\text{RL}}
\newcommand\DATE{\mathbb{D}\text{ATE}}
\newcommand\RECORD{\mathbb{R}\text{ECORD}}
\begin{equation*}
  \begin{split}
    NewCrawl:    &~ \URL \rightarrow \mathcal{P}(\RECORD)\\
    UpdateCrawl: &~ \URL \times \DATE \rightarrow \mathcal{P}(\RECORD)
  \end{split}
\end{equation*}
%
where $\URL$, $\DATE$ and $\RECORD$ are respectively the set of all URLs, dates and records, and $\mathcal{P}$ designates the powerset operator. By delegating all shared mutable state to the back end system, web crawler instances can be added, removed and used interchangeably.
